---
title: "Teff_draft"
output: html_document
date: "2023-05-21"
editor_options: 
  markdown: 
    wrap: 72
---

## Setup

```{r}
library(fastDummies) 
library(tidyverse)
library(dbplyr)
```

## Import data

```{r}
teff_input_use<- read.csv("https://raw.githubusercontent.com/Chihirono/Capstone/main/sectionf3_teffinputuseduringcultivation.txt")
teffsales <- read.csv("https://raw.githubusercontent.com/Chihirono/Capstone/main/sectiong_teffsales.txt")
householdroster <- read.csv("https://raw.githubusercontent.com/Chihirono/Capstone/main/sectiona_householdroster.txt")
landownershipandcultivationtypeofparcels <- read.csv("https://raw.githubusercontent.com/Chihirono/Capstone/main/sectionb_landownershipandcultivationtypeofparcels.txt")
sectionn_assets <- read.csv("https://raw.githubusercontent.com/Chihirono/Capstone/main/sectionn_assets.txt")
sectiono_livestockownership <- read.csv("https://raw.githubusercontent.com/Chihirono/Capstone/main/sectiono_livestockownership.txt")
sectionc_landsizesacquisitionandtenure <- read.csv("https://raw.githubusercontent.com/Chihirono/Capstone/main/sectionc_landsizesacquisitionandtenure.txt")
```

# Teff input (independent variable)

## Check data

```{r}
names(teff_input_use)
teff_input_use <-rename(teff_input_use, percel_no = "sectionf31",teffplotno = "sectionf32",dap_quintals = "sectionf33",urea_quintals = "sectionf35")
summary(teff_input_use)
```

# Teff input (dependent variable)

## Make a column of the quantitiy of chemical fertilizer ( dap_quintals + urea_quintals)

```{r}
teff_input_use <- mutate(teff_input_use,chemical_fertilizer = teff_input_use$dap_quintals+teff_input_use$urea_quintals)

teff_chemical_dependent <- teff_input_use%>%
  group_by(hhid) %>% summarise(sum_fertilizer_hhid = sum(chemical_fertilizer))
teff_chemical_dependent <-as.data.frame(teff_chemical_dependent)

```

# Teff transportation cost (independent variable)

## Check data

```{r}
teffsales <- rename(teffsales, total_cost_transportation = sectiong15, transactionno = sectiong1)
summary(teffsales)

#length(unique(teffsales$hhid))

```

## get a total transportation cost group by house hold id. (hhid)

```{r}
sum_transportation <- teffsales%>%
  group_by(hhid) %>% summarise(sum_transportationcost_hhid = sum(total_cost_transportation))
sum_transportation <-as.data.frame(sum_transportation)

```

## Devide transportation cost by percel of each household

```{r}
#Check the number of transaction of each household
summary(teffsales$transactionno) #column "transactionno" includes some na.
```

```{r}
#Check the contents of na
na_transactioncostcost <- as.data.frame(table(teffsales[is.na(teffsales$transactionno),"hhid" ]))
colnames(na_transactioncostcost ) <- c("hhid","number_of_na_for_transaction_cost")
table(na_transactioncostcost)
```

The table shows - hhid of 114,515,708　has 9 missing value, probably by
mistake. 1. not count these 9 missing value to divide total transaction
cost of each hh.

-   Other hhid that has one missing value in transaction cost answered
    that they did not have any transaction (column:"sectiong0=0").

2.  not include for regression analysis because they can't show the
    relationship between transportation cost and input.

```{r}
#1. not count these 9 missing value to divide total transaction cost of each hh.
error_na_for_parcel_amount_removed<-as.data.frame((teffsales[!(teffsales$sectiong0==1 & is.na(teffsales$transactionno)),]))
no_of_percel_for_each_household<-as.data.frame(table(error_na_for_parcel_amount_removed$hhid))
colnames(no_of_percel_for_each_household) <-c("hhid","no_of_parcel")
summary(no_of_percel_for_each_household) # check if the maximum of parcel number is 5 (consistent with the survey)
no_of_percel_for_each_household$hhid<-as.numeric(no_of_percel_for_each_household$hhid)
```

```{r}
average_transportation_cost_per_percel<-inner_join(sum_transportation,no_of_percel_for_each_household, by = "hhid")
average_transportation_cost_per_percel<-mutate(average_transportation_cost_per_percel,average_transportation_cost=average_transportation_cost_per_percel$sum_transportationcost_hhid/average_transportation_cost_per_percel$no_of_parcel)
average_transportation_cost_per_percel$average_transportation_cost<-round(average_transportation_cost_per_percel$average_transportation_cost,1)
names(average_transportation_cost_per_percel)
transportation_independent<-select(average_transportation_cost_per_percel,hhid,average_transportation_cost)
```

## Combine dependent variable and independent variable based on household id(hhid)

```{r}
chemical_transportation <- inner_join(transportation_independent,teff_chemical_dependent, by = "hhid")
```

## Do regression analysis

```{r}
fertilizerinput_model1 <-
  lm(sum_fertilizer_hhid~average_transportation_cost,data= chemical_transportation)
  
  
  #lm(minutes~scale(n_previous_marathons)+scale(age)+scale(hills)+Male+Female+Sunny+Cloudy+Heavy_Rain,data=Marathon_Time_df)
summary(fertilizerinput_model1)

```

## Household infromation (<data:householdroster>)

What we need is -sex of the head of household - age of the head of
household - education level of head of household

ID　code1 is the head of house hold -\> take the sex (male = 1) and age
of each ID code1 Then recode the education level into number.

### Make a column of sex and age

性別と年齢の

```{r}
householdroster <-rename(householdroster, ID_code = sectiona1,
                        sex = sectiona2,
                        age = sectiona3)
householdroster1 <-subset(householdroster,householdroster$ID_code==1)
householdroster1 <-dummy_cols(householdroster1,select_columns = "sex")

```

### Make a column of education level.

```{r}
#1. check the value and its number inside the original columns.
table_edu <- as.data.frame(table(householdroster1$sectiona7))
table_edu

ggplot()+geom_bar(data=table_edu, aes(x = Var1, y = Freq,fill="Frequency"),
            linewidth = 1, width = 0.4, stat="identity", position="identity")+theme_bw()+theme(text=element_text(size=14),legend.position = c(0.98, 0.98),legend.justification = c(0.48, 0.48), legend.background=element_rect(fill="white"))+ggtitle("Histogram of education level")+xlab("Education level")+ylab("Number of people")+theme(plot.title = element_text(hjust =0.5))+theme(legend.position="top")+theme(legend.title=element_blank())+theme(axis.text.x = element_text(size = 10, angle = -30, vjust = 0.5, hjust = 0))
```

```{r}
unique(householdroster1$sectiona7)
```

As the number of "","adult literacy program", "some church/mosque
school" ,"other literacy program" are not dominant, these category is
replaced with missing value and these household ID will be disregarded
for regression.

"completed higher education (not university)" -\>9 "incomplete higher
education (not university)"-\>8(average of 7.8.9) check the number of
values below "adult literacy program" -\>remove the row "some
church/mosque school" -\>remove the row "other literacy program"
-\>remove the row

```{r}
householdroster1 <- mutate(householdroster1, educationlevel = recode(sectiona7,
                                                                     "1st grade"=1,
                                                                     "2nd grade"=2,
                                                                     "3rd grade"=3,
                                                                     "4th grade"=4,
                                                                     "5th grade"=5,
                                                                     "6th grade"=6,
                                                                     "7th grade"=7,
                                                                     "8th grade" =8,
                                                                     "9th grade"=9,
                                                                     "10nth grade"=10,
                                                                     "11th grade"=11,
                                                                     "12th grade" =12,
                                                                     "incomplete higher education (not university)"=8,
                                                                     "completed higher education (not university)"=9,
                                                                     "did not complete any schooling"=0
                                                                     
                                                                  ))

householdroster1
gender_age_education_independet<-select(householdroster1,hhid,sex_male,age,educationlevel)
```

```{r}
size_of_household <- table(householdroster$hhid) 
size_of_household <-as.data.frame(size_of_household)
colnames(size_of_household ) <- c("hhid","size_of_hh")  # change column names of all the columns in the dataframe 
size_of_household$hhid <-as.numeric(size_of_household$hhid) #change data hhid into numeric to combine data frames later as an independent variable
summary(size_of_household)
size_of_household 

```

### if the household own donkey

```{r}
table(sectiono_livestockownership$sectiono1) #Check if each household indicates ownership status of donkey
donkey <-subset(sectiono_livestockownership,sectiono_livestockownership$sectiono1=="donkeys")# Aggregate by the row donkey
donkey <-dummy_cols(donkey,select_columns = "sectiono3")
donkey <- select(donkey,1,7) #choose column needed for the regression
names(donkey)
donkey<- rename(donkey, own_donkey = sectiono3_yes)

```

### if the household own mobile phone

```{r}
table(sectionn_assets$sectionn1) #Check if each household indicates ownership status of mobile phone
mobile_phone <-subset(sectionn_assets,sectionn_assets$sectionn1=="mobile phone")# Aggregate by mobile phone
mobile_phone <-dummy_cols(mobile_phone,select_columns = "sectionn3")
mobile_phone <- select(mobile_phone,1,7) #choose column needed for the regression
mobile_phone<- rename(mobile_phone, own_mobile_phone = sectionn3_yes)
```

```{r}
landownershipandcultivationtypeofparcels<- rename(landownershipandcultivationtypeofparcels, ha_cultivated_by_hh_or_not_cultivated= sectionb7,
                        ha_cultivated_by_anotherhh = sectionb11)

#replace na of the ha of land owned with 0 
landownershipandcultivationtypeofparcels[is.na(landownershipandcultivationtypeofparcels$ha_cultivated_by_hh_or_not_cultivated),]$ha_cultivated_by_hh_or_not_cultivated <- 0
landownershipandcultivationtypeofparcels[is.na(landownershipandcultivationtypeofparcels$ha_cultivated_by_anotherhh),]$ha_cultivated_by_anotherhh <- 0

summary(landownershipandcultivationtypeofparcels)
#landownershipandcultivationtypeofparcels<-mutate(landownershipandcultivationtypeofparcels,land_owned_per_each_property = ha_cultivated_by_hh_or_not_cultivated + ha_cultivated_by_anotherhh)


land_owned <- landownershipandcultivationtypeofparcels%>%group_by(hhid) %>% summarise(sum_ha_cultivated_by_hh_or_not_cultivated = sum(ha_cultivated_by_hh_or_not_cultivated),sum_ha_cultivated_by_anotherhh = sum(ha_cultivated_by_anotherhh))
land_owned <-as.data.frame(land_owned)


land_owned <-mutate(land_owned, total_land_owned = sum_ha_cultivated_by_hh_or_not_cultivated + sum_ha_cultivated_by_anotherhh)
land_owned_independent <- select(land_owned,hhid,total_land_owned)             
```

## Dependent variable total cultivated parcels

To divide chemical use per cultivated parcel

```{r}
summary(sectionc_landsizesacquisitionandtenure)
total_ha_cultivated <- sectionc_landsizesacquisitionandtenure %>% group_by(hhid) %>% summarise(sum_total_ha_cultivated = sum(sectionc2c))
total_ha_cultivated <-as.data.frame(total_ha_cultivated)
total_ha_cultivated<-select(total_ha_cultivated,hhid,sum_total_ha_cultivated)

```

## Make dependent variable2

This time, dependent variable is total fertilizer divided by the ha of
cultivated land per each household.

```{r}
teff_chemical_devided_by_ha <- inner_join(teff_chemical_dependent,total_ha_cultivated, by = "hhid")
teff_chemical_devided_by_ha <-mutate(teff_chemical_devided_by_ha,teff_chemical_devided_by_ha=sum_fertilizer_hhid/sum_total_ha_cultivated)
teff_chemical_ha_dependent2<-select(teff_chemical_devided_by_ha,c(1,4))
teff_chemical_ha_dependent2 #This is the dependent variable for the second analysis
```

## Make independent variable 2

```{r}

teff_independent2 <- transportation_independent %>%
  inner_join(gender_age_education_independet,by="hhid") %>% 
  inner_join(size_of_household,by="hhid") %>% 
  inner_join(mobile_phone,by="hhid") %>%
  inner_join(donkey,by="hhid") %>% 
  inner_join(land_owned_independent,by="hhid")

```

### Make data frame for the model2

```{r}
chemical_transportation_df2 <- inner_join(teff_chemical_ha_dependent2,teff_independent2, by = "hhid")
names(chemical_transportation_df2)
```

### Regression analysis 2

-   Dependent variable:chemical input divided by ha for each household
-   Independent:

1.  Average transportation cost
2.  Gender of household head
3.  Education level of of household head
4.  size of household
5.  If household own mobile phone
6.  If household own donkey
7.  Total land owned by household

```{r}
chemical_transportation_df2$age <-as.numeric(chemical_transportation_df2$age)
fertilizerinput_model2 <-
  lm(teff_chemical_devided_by_ha~average_transportation_cost+sex_male+age+educationlevel+size_of_hh+own_mobile_phone+own_donkey+total_land_owned,data= chemical_transportation_df2)
summary(fertilizerinput_model2)
```

### Z sores of Regression analysis 2

```{r}
z_scores_fertilizerinput_model2 <- scale(coef(fertilizerinput_model2))
z_scores_fertilizerinput_model2
```

### Regression analysis 3

-   Dependent variable: Sum of chemical input for each household
-   Independent:

1.  Average transportation cost
2.  Gender of household head
3.  Education level of of household head
4.  size of household
5.  If household own mobile phone
6.  If household own donkey
7.  Total land owned by household

```{r}
chemical_transportation_df3 <- inner_join(teff_chemical_dependent,teff_independent2, by = "hhid")
chemical_transportation_df3$age <-as.numeric(chemical_transportation_df3$age)
fertilizerinput_model3 <-lm(sum_fertilizer_hhid~average_transportation_cost+sex_male+age+educationlevel+size_of_hh+own_mobile_phone+own_donkey+total_land_owned,data= chemical_transportation_df3)
summary(fertilizerinput_model3)
```

### Z sores of Regression analysis 3

```{r}
z_scores_fertilizerinput_model3 <- scale(coef(fertilizerinput_model3))
z_scores_fertilizerinput_model3
```

## Conclusion

-   Regression analysis 2 indicates that average transportation cost
    does not influence the amount of average chemical input.
-   Regression analysis 3 indicates that average transportation cost
    influence the amount of total chemical input.

```{r}
regression2_without_na <- na.omit(chemical_transportation_df2)

fertilizerinput_model2_without_na <- lm(teff_chemical_devided_by_ha~average_transportation_cost+sex_male+age+educationlevel+size_of_hh+own_mobile_phone+own_donkey+total_land_owned,data= regression2_without_na)
summary(fertilizerinput_model2_without_na)
```
